Scheduling and Amortization for MPC

### 2022-02-09 biometric_vectorization_example.tex
Added a TODO in Basic Vectorization.

>>>>

\ana{TODO: It will be good to add a pass in Phase 3 to get rid of extra dimensionality. 
Once we have vectorized as much as possible, there is no need to keep higher 
dimensionality. E.g., there is no need for the 2-dimensional array sum in the first for loop, 
and similarly, there is no need for 1-dimensional arrays for min\_sum and min\_index.
We should get rid of these before generating MOTION code.}
